Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2014-07-07 tex/ms.tex
more model notation tweaks

\subsection{Star Cluster Model}
We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by
\begin{eqnarray}\displaystyle
F_{\theta^\prime}(\lambda_o) & = &
\frac{m_*}{4\pi d_L^2(1+z)} \, S(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V} \\
\nonumber \\ 
\lambda_o & = & (1+z)\,\lambda 
\\
\theta^\prime & \equiv & \left[ m_*, t, Z, \tau_V, z, d_L, \beta, \right]
\quad ,
\end{eqnarray} where the
parameters $\theta^\prime$ include the stellar mass $m_*$, effective optical
depth to dust in the $V$-band $\tau_V$, luminosity distance $d_L$,
and redshift $z$.  The obsrved frame wavelengths $\lambda_o$ are
related to the restframe wavelengths $\lambda$ in the usual way.

@@

The final mean model is then given by 
\begin{eqnarray}\label{eq:MeanModel} 
\mu(\theta, \lambda_o) &  = & (G_\sigma  \otimes F_{\theta^\prime})(\lambda) +
\sum_{\ell=0}^{N_\ell} S_\ell \\
S_\ell & = & \frac{A_\ell}{\sigma_e\sqrt{2\pi}} \exp(-\frac{(\lambda -
 \lambda_\ell)^2}{2\sigma_e^2})\\
\theta & \equiv & \left[ \{\theta^\prime\}, \sigma, \{A_\ell\}_{\ell=0}^{N_l},
  \sigma_e \right]
\quad ,
\end{eqnarray}
where $G$ represents a Gaussian of unit area, $\otimes$ indicates
convolution, and the full parameter set $\theta$ now includes the
amplitudes of the $N_l$ nebular and interstellar emission lines
$A_\ell$.  We again implicitly include the conversion from restframe
to observed frame spectra.

>>>>

\subsection{Star Cluster Model}
We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by
\begin{eqnarray}\displaystyle
F_{\theta^\prime}(\lambda_o) & = &
\frac{m_*}{4\pi d_L^2(1+z)} \, S(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V} \\
\nonumber \\ 
\lambda_o & = & (1+z)\,\lambda 
\\
\theta^\prime & \equiv & \left[ m_*, t, Z, \tau_V, z, d_L, \beta \right]
\quad ,
\end{eqnarray} where the
parameters $\theta^\prime$ include the stellar mass $m_*$, effective optical
depth to dust in the $V$-band $\tau_V$, luminosity distance $d_L$,
and redshift $z$.  The obsrved frame wavelengths $\lambda_o$ are
related to the restframe wavelengths $\lambda$ in the usual way.

@@

The final mean model is then given by 
\begin{eqnarray}\label{eq:MeanModel} 
\mu(\theta) &  = & (G_\sigma  \otimes F_{\theta^\prime})(\lambda) +
\sum_{\ell=0}^{N_\ell} S_\ell \\
S_\ell & = & \frac{A_\ell}{\sigma_e\sqrt{2\pi}} \exp(-\frac{(\lambda -
 \lambda_\ell)^2}{2\sigma_e^2})\\
\theta & \equiv & \left[ \{\theta^\prime\}, \sigma, \{A_\ell\}_{\ell=0}^{N_l},
  \sigma_e \right]
\quad ,
\end{eqnarray}
where $G_\sigma$ represents a Gaussian of unit area and standard
deviation $\sigma$, $\otimes$ indicates convolution, and the full
parameter set $\theta$ now includes the dispersion $\sigma_e$ and
amplitudes $A_\ell$ of the $N_l$ nebular and interstellar emission
lines.
